### 2024-10-29 paper/3-motivation.tex
Add todo
Change function name

\red{TODO: remove redundant part in the fig} \\
\red{TODO: explanation of context(frame/label): in the background? or here?} \\
\red{TODO: the notion of meta-level interpreter in background} \\

@@

% an example of function call in official prose
\textbf{Example 3}
\begin{verbatim}
  // function definition as follow
  (func $foo (result i32) (i32.const 42))

  // function call
  (call $foo) (f32.const 3.14)
\end{verbatim}

>>>>

\red{TODO: explanation of the terms \officialp{} and \spectecp{}} \\
\red{TODO: remove redundant part in the fig} \\
\red{TODO: explanation of context(frame/label): in the background? or here?} \\
\red{TODO: the notion of meta-level interpreter in background} \\
\red{TODO: try finding better terminology rather than "model"} \\

@@

% an example of function call in official prose
\textbf{Example 3}
\begin{verbatim}
  // function definition of $push-42
  (func $push-42 (result i32) (i32.const 42))

  // function call
  (call $push-42) (f32.const 3.14)
\end{verbatim}
